RepData_PeerAssessment1
========================================================

##Loading and preprocessing the data
```{r}
data<-read.csv("activity.csv")
```

##The total number of steps taken per day
```{r}
total_steps<-aggregate(steps~date, data=data, na.rm=T)
hist(total_steps$steps)
```

##The mean and median total number of steps
```{r}
mean_steps<-mean(total_steps$steps)
median_steps<-median(total_steps$steps)
```


##The average daily activity pattern
```{r}
aver_pattern<-aggregate(steps~interval, data=data, FUN=mean)
plot(aver_pattern, type="l",main="Average Daily Activity Pattern", xlab="5 Mins Intervals Daily", ylab="Average Steps All Days")
```

##Imputing missing values
###Total number of missing values
```{r}
missing_total<-sum(is.na(data))
```

###Create a vector store steps with NAs
```{r}
imputed_steps<-numeric()
for(i in 1:nrow(data)){
x<-data[i,]
if (is.na(x$steps)){
y<-sbuset(aver_pattern,interval==x$interval)$steps
}
else
{
y<-x$steps
}
imputed_steps<-c(imputed_steps,y)
}
```

###Create a new dataset equal to the original dataset with the missing data
```{r}
imputed_data<-data
imputed_data$steps<-imputed_steps
imputed_steps_perday<-aggregate(steps~date, data=imputed_data, FUN=sum)
```

```{r}
hist(imputed_steps_perday$steps, breaks=nrow(imputed_steps_perday),main="Total Steps Per Day with Imputed",xlan="Steps perday",col="red")
```

###Mean median total number of steps per day
```{r}
mean_imputed_steps<-mean(imputed_steps_perday$steps)
median_imputed_steps<-median(imputed_steps_perday$steps)
```

##Differences in activity patterns between weekdays and weekends
```{r}
imputed_data$date<-as.date(imputed_data$date)
weekend<-c("Sat","Sun")
imputed_data$daytype<-as.factor(sapply(imputed_data$date,function(x) ifelse(weekdays(x) %in% weekend,"weekend","weekday")))
```

```{r}
require(plyr)
average_steps<-ddply(imputed_Data,.(interval,daytype), summarize,  steps=mean(steps))

require(lattice)
xyplot(steps~interval | daytype, data=average_steps, layout=c(1,2),type="l",xlanb="5 mins intervals over day", ylab="Number of steps", main="Activity Patterns on weekdays and weekends")

